### 2021-02-10 manuscript.tex
finalized results outline

\subsection{Architecture Upgrades}
previous installation used traditional lamp stack

@@

Interface improved. Table content contained within single page.

The rebuilt data integration process represents a core accomplishment of the refactoring project. A reconstruction of this process and the frameworks utilized to execute it offered notable improvements

Improvements to the core achritecture stand as the central accomplishments in undertaking this project.

@@

\subsection{Resource Utilization Improvements}
Space constraints eliminated. Server resource reqs reduced overall.

>>>>

\subsection{Architecture Upgrades}

Accomplished project goals

Design

Table interface now streamlined to single page

New admin tools streamline app control

Site render automated.

Better url

The rebuilt data integration process

Architecture

implemented modern web platform (front-end and table app) from lamp stack

upgraded server from rhel6

Performance/resources

Space constraints eliminated.

Server resource reqs reduced overall.

Data files made dynamic and transient

@@

@@

\subsection{Resource and Design Improvements}

Design, architecture, performance

Space constraints eliminated. Server resource reqs reduced overall.
